---
title: "Alcohol vs Seat choice"
author: "Giovanni Asencio"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
davisdata %>%
 group_by(Seat) %>%
 summarise(
   Mean = mean(alcohol),
   SD = sd(alcohol),
   Count = n()
 )
``` 
Students sitting in the back row appear to consume the most alcohol on average. Students sitting in the front row consume the least alcohol on average.
## Inferential Tests
```{r}
anova_model <- aov(alcohol ~ Seat, data=davisdata)

summary(anova_model)
```
```{r}
TukeyHSD(anova_model)
```
## Conclusions
The ANOVA test will determine whether there is evidence that average alcohol consumption differs among seating rows. TukeyHSD will identify which rows differ from one another.

